---
title: "(graphic_description)"
description: |
  A short analyse of some data about zooplankton. 
author:
  - name: Clemence Coquillart
    url: {}
date: 11-18-2020
output:
  distill::distill_article:
    self_contained: false
categories  :
  - Data Sciences I
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r setup}
SciViews::R
```

```{r importation}
data <- data("zooplankton", package = "data.io")
```

# Introduction 

Here are a short analyse about the morphology of zooplankton. Most especially about the area they occupy and their size. The graphic I propose will show us if it exist a link between these two characteristics. 

# Analyse

```{r retirer valeur extreme}
zooplankton <- filter(zooplankton, density < 1,5)
```


```{r graphique}
chart(data = zooplankton, area ~ size %col=% class) +
  geom_point(alpha = 0.5)
```
  
  We can observe that there is indeed a link between the size and the area. The more zooplankton occupy a high area, the more they have a big size. The evolution tend to be exponential. We can also see that the class of the Chaetognath is the class that have the biggest size while occupying a short area in contrast with the other classes. The biggest zooplankton that can reach the biggest connection between the area and the size are from the class "Chidarian". 

.
